### 2015-05-13 whoop.tex
A few more thoughts

\medskip\noindent\textbf{Watchdog Summarization }
%
Early in the development of \whoop we experimented with reasoning about recursion-free drivers by resorting to full inlining.  We found that this did not scale to large drivers: when we tried to apply \whoop to the r8169 ethernet driver ($>$7000 lines of C code) with all functions fully inlined, we quickly exhausted the memory limits of our experimental platform.  \ADComment{Is it thus the case that r8169 did not exhibit any recursion?}  The C-to-Boogie translation produced, after inlining, hundreds of thousands of lines of Boogie IVL code, consuming a lot of memory and leading to gigantic verification conditions that the Z3 theorem prover could not handle effectively.  \ADComment{I rephrased the previous sentence, because if I remember correctly we did get to the point of invoking Z3.  But maybe I imagined that - perhaps we could not even generate the VC?}  Furthermore, some entry points invoke recursive helper functions, which cannot be fully inlined.

@@

>>>>

\medskip\noindent\textbf{Watchdog Summarization }  \ADComment{Due to my thoughts below, I'm unsure about calling this ``Watchdog'' summarization, as I don't think we're doing anything new here.  I think perhaps ``Generatino of Loop and Procedure Summaries'' would be better.}
%
Early in the development of \whoop we experimented with reasoning about recursion-free drivers by resorting to full inlining.  We found that this did not scale to large drivers: when we tried to apply \whoop to the r8169 ethernet driver ($>$7000 lines of C code) with all functions fully inlined, we quickly exhausted the memory limits of our experimental platform.  \ADComment{Is it thus the case that r8169 did not exhibit any recursion?}  The C-to-Boogie translation produced, after inlining, hundreds of thousands of lines of Boogie IVL code, consuming a lot of memory and leading to gigantic verification conditions that the Z3 theorem prover could not handle effectively.  \ADComment{I rephrased the previous sentence, because if I remember correctly we did get to the point of invoking Z3.  But maybe I imagined that - perhaps we could not even generate the VC?}  Furthermore, some entry points invoke recursive helper functions, which cannot be fully inlined.

@@

\ADComment{In the above, can you make it super-clear that it is fine for the candidates to be wrong: Houdini will just kick them out?  You might want to look at the comment on this in the GPUVerify 2012 OOPSLA paper; I remember writing something nice along these lines, feel free to re-use it.  If you search for Houdini you'll find it.}
